%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Tommy P. Keane
% Master of Science Thesis
% Department of Electrical and Microelectronic Engineering
% Rochester Institute of Technology
%
% April 2011
%
%
%
% Funded By: Lenel Systems Inc., A UTC Fire & Security Corporation
%
% Algorithm Intellectual Property Owned By: Lenel Systems Inc.
%
%
% http://www.tommypkeane.com
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHAPTER 3
%
% SECTION 1.3: Weighted and Filtered Mutual Information
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN DOCUMENT

This stage of the algorithm is part of the affine search stage, so it should be kept in mind that the following calculations are re-occurring at each point in the search through the skew-scale-rotation-space. This must be the most efficient stage in the algorithm because it occurs so many times, but it is also the core of the algorithm that is the limitation for the accuracy. This section is the most important in understanding the trade-offs between accuracy and efficiency.

Up to this point the discussion of mutual information has described it as a measure based on random variables. Those random variables were then attributed to the digital color images. But in the actual implementation, it is performed on the maps of the ``edge'' values from each view. But it is not just the mutual information between the two images that is being calculated, it is the mutual information between every possible rectangular overlap between the two images (an exhaustive translation search). This makes the mutual information a mapped measurement, meaning that ...


By applying a non-translational affine transformation (i.e. a combination of skewing, scaling, and rotation) the images can be put through a brute force translation search that creates a mutual information measurement for each translation, since each translation provides a new overlap region with the feature images.

Map size $M \times N = (2\mathfrak{m}-1) \times (2\mathfrak{n}-1)$

\begin{equation}
\label{WeightedInformation}
	I_{w}(A,B)=w(A,B) \cdot I(A,B)
\end{equation}


\begin{equation}
\label{}
w(A,B)=\sum_{j}\sum_{i}{h_{A}(a_{i})h_{B}(b_{j})}
\end{equation}


\begin{equation}
\label{}
A_{u}=\{x,y\}_{u} \rightarrow \left\{ \mathcal{O}_{T}\left(\mathcal{A}(x,y) \right) \right\}_{u} 
\end{equation}


\begin{equation}
\label{}
B_{v}=\{x,y\}_{v} \rightarrow \left\{ \mathcal{O}_{T}\left(\mathcal{A}(x,y) \right) \right\}_{v}
\end{equation}


\begin{equation}
\label{}
\mathfrak{w}(A,B)=\sum_{j}\sum_{i}{h_{A_{u}}(a_{i})h_{B_{v}}(b_{j})}
\end{equation}

\begin{equation}
\label{}
\mathfrak{I}(u,v)=I(A_{u},B_{v})=\left(\frac{2}{H(A_{u})+H(B_{v})}\right)
\end{equation}


\begin{equation}
\label{WeightedInformation}
	\mathfrak{I}_{\mathfrak{w}}(u,v)=\mathfrak{w}(u,v) \cdot \mathfrak{I}(u,v)
\end{equation}


\begin{equation}
\label{laplacianFilter}
	L(u,v)=\frac{4}{(\alpha + 1)} \cdot
	\begin{bmatrix}
		\frac{\alpha}{4} & \frac{(1-\alpha)}{4} & \frac{\alpha}{4} \\
		\frac{(1-\alpha)}{4} & -1 & \frac{(1-\alpha)}{4} \\
		\frac{\alpha}{4} & \frac{(1-\alpha)}{4} & \frac{\alpha}{4}
	\end{bmatrix}, \quad \alpha \in [0,1)
\end{equation}

\begin{equation}
\label{FilteredWeightedInformation}
	\mathfrak{I}_{L\mathfrak{w}}(u,v)=L(u,v) \ast \mathfrak{I}_{\mathfrak{w}}(u,v)
\end{equation}

\begin{equation}
\label{peakLocation}
	(\delta_{x},\delta_{y})=\max_{u,v}\left(\mathfrak{I}_{L\mathfrak{w}}\right)
\end{equation}

\begin{equation}
\label{peakTranslation}
	(t_{x},t_{y})=(k,l) \cdot \left| (\delta_{x},\delta_{y}) - (M,N) \right|
\end{equation}

\begin{equation}
\label{peakTranslation}
	[k,l] = \left[ \left| (\delta_{x},\delta_{y}) - (M,N) \right| \le (M,N) \right] - [1,1]
\end{equation}

From the vector Equation \ref{peakTranslation}, $k$ and $l$ will be either $-1$ or $1$.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF DOCUMENT

