%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Tommy P. Keane
% Master of Science Thesis
% Department of Electrical and Microelectronic Engineering
%
% March 2011
%
%
%
% .tex and .sty modified from:
% http://www.ce.rit.edu/studentresources/gradresource/LaTexThesis.zip
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHAPTER 1
%
% PREAMBLE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN DOCUMENT
Before delving into the depths the algorithm, its development, its implications, its contributions, its results, and its potential future, there needs to be an introduction to what has been, and what is trying to be, achieved here. Mathematics and programming are languages, they are functional, and they are tools to serve a purpose. Without understanding that purpose, without preparation and a solid foundation, there would be nothing but a set of facts and figures susceptible to misinterpretation. The core of the WFMI algorithm is in its implementation of very well understood standard processes and operations, thus it is not a new type of operation. A lot of the following discussion is then focused on explaining where the application of these operations follows from and why and when it succeeds or fails. In order to maintain a clear and consistent understanding the following terms and phrasings will be used.

A \textbf{scene} is understood here as the real-world location being imaged, and the camera imaging the scene is known as the \textbf{view} (of the scene). The output of the camera is understood to be a digital tri-chromatic video composed of tri-chromatic (typically RGB) \textbf{frames}. The most important term will be the overlap between views. In this context we are defining overlap to mean the regions within the views’ frames which have imaged the \textit{same region} within the scene. As will be discussed, characteristics of imaging geometry (parallax, occlusion, etc.) will not allow for identical overlap regions in the frames, but our definition will apply to the understanding that there is real-world correspondence between the imaged objects from the scene onto the frames through the views and the regions of the scene present in the real-world as observed by views and captured in their frames. The application of the WFMI algorithm is to accurately register frames from views of these complex scenes based on scene-object information, not purely on pixel-to-pixel registration between frames.

First it is necessary to present an understanding of the current state of research in the field of realistic scene image registration and then develop the beginnings of the algorithm.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF DOCUMENT
