%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Tommy P. Keane
% Master of Science Thesis
% Department of Electrical and Microelectronic Engineering
% Rochester Institute of Technology
%
% April 2011
%
%
%
% Funded By: Lenel Systems Inc., A UTC Fire & Security Corporation
%
% Algorithm Intellectual Property Owned By: Lenel Systems Inc.
%
%
% http://www.tommypkeane.com
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHAPTER 6
%
% SECTION 2: FINAL REMARKS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN DOCUMENT

Again, the work completed here was initially attempting to create a fully automatic panorama creation algorithm from overlapping views of an unknown scene at unknown locations with unknown cameras. While this initial goal cannot be described as being completely met, what has been produced is a novel application of mutual information as a metric in image registration, as it has extended beyond well-defined affine scenarios with large amounts of overlap in well-conditioned views of simple scenes. It is a robust and accurate algorithm for affine views and is an intelligent estimate when extended to projective views of complex, realistic scenes. This work shows the beginnings of extending the known robustness of mutual information as a metric for image and video data correspondence. There are many avenues in which to extend this research that progress in line with modern research as digital imagery is being view more and more as holding extensive amounts of information beyond the reach of basic intensity and gradient calculations. There is also no limitation to the applications where the WFMI algorithm can be used in conjunction with point-to-point algorithms to find the true homography between views. Especially considering that this is video data, the WFMI algorithm can be applied to the first frames and a much simpler point-to-point algorithm can take advantage of these initial conditions and present a completely accurate panorama. Coupled with the potential for real-time operation, the WFMI algorithm can quickly and efficiently create an accurate registration estimate, that can then be immediately adapted to be more accurate and present a viewer with the most accurate result without any knowledge of the scene and by avoiding the complex computations of point-to-point algorithms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF DOCUMENT

